Process_MCData

### 2024-01-23 Code/Process_MCData.Rmd
Uncommented chunk

Run for each file in a session; all chunks below run for each file.
```{r read ProcessFile}
ProcessFile <- "../Data/ImportedData/ImportedMCData/20231026_PICO_MCMIX006_RUN126_TargetDataMetaFilter.Rds"

@@

# ProcessData <- ProcessData %>%
#   filter(Strain == "SS120" & time >= InitialTime |
#          Strain == "MIT9313" |
#          Strain =="MED4"  )

>>>>

Run for each file in a session; all chunks below run for each file.
```{r read ProcessFile}
ProcessFile <- "../Data/ImportedData/ImportedMCData/20220824_PICO_MC257_RUN86_TargetDataMetaFilter.Rds"

@@

ProcessData <- ProcessData %>%
  filter(Strain == "SS120" & time >= InitialTime |
         Strain == "MIT9313" |
         Strain =="MED4"  )
